\mytitle{}

### 2018-07-10 paper/paper.tex
Stop repeatedly saving & loading stats

?? TCP perf characteristics under packet drop known by the Mathis equation \cite{DBLP:journals/ccr/MathisSMO97}:
$$ \operatorname{BW} = \frac{\operatorname{MSS}}{\operatorname{RTT}} \frac{C}{\sqrt{p}},$$
for the \emph{maximum segment size} (MSS), \emph{round trip time} (RTT), a choice of constant $C$ dependent on system assumptions and the probability $p \in (0, 1]$ that a packet is lost.

>>>>

?? TCP perf characteristics under packet drop known by the Mathis equation \cite{DBLP:journals/ccr/MathisSMO97}:
$$ \operatorname{BW} = \frac{\operatorname{MSS}}{\operatorname{RTT}} \frac{C}{\sqrt{p}},$$
for the \emph{maximum segment size} (MSS), \emph{round trip time} (RTT), a choice of constant $C \approx{} \sqrt{3/2}$ dependent on system assumptions and the probability $p \in (0, 1]$ that a packet is lost.
The lower bound on $p$ is deliberately open, as packet drop acts as a control signal for the TCP send window size.
